Quantile Regressions via Method of Moments with multiple fixed effects

### 2023-10-30 article/article.qmd
mmqreg
update

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 1p
      cite-style: authoryear
---

@@

A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data. However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem. While many strategies have been proposed for estimating this type of model (see Galvão and Kato, 2018 for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.

@@

In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005, @mss2019, @he1997 and @zhao2000 ), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d. error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors, as well.

@@

$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
$$ {#eq-eq3}

@@

In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_th$ unconditional quantile of the standardized error $\varepsilon$.

@@

While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model. First, because the location and scale model can be identified globally, with only a single parmater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000). Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.

@@

3.  Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $e$ can be estimated using the following condition:

@@

Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.

@@

$$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
$$

@@

While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately. The variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).

1. Need to add the general condition Var=(inf (theta) * inf(theta))

Thatn inf(theta) = inf beta gamma and q)tay

and finally define what the IFs are (see appendix)

@@

Cross product of IFs

@@

Sun then cross product

@@

Original paper;

@@

2.  We estimate the location model using the centered-residualized variables:

$$y_{i}^{rc} = x_{i}^{rc'} \beta + nu_{i}
$$

@@

$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + e_{i}$$

@@

$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat e_{i}}$$

where $|\hat\nu_{i}|- \hat e_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$

@@

# Monte Carlo Simulations

# Application: **Something interesting**

@@

# Appendix {.appendix}

>>>>

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 1p
      cite-style: authoryear
      number-depth: 2

---

@@

A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data. However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem. While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.

@@

In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@cameron2005, @mss2019, @he1997,  @zhao2000], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d. error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors, as well.

@@

$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
$${#eq-eq3}

@@

In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.

@@

While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model. First, because the location and scale model can be identified globally, with only a single paramater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000). Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.

@@

3.  Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:

@@

Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations evaluated at $\hat\theta$.

@@

$$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
$${#eq-eqqtile}

@@

While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately. Afterwards, the variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).

Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as:
$$\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
$${#eq-eqvcv}

where the influence functions are defined as:

$$\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)$$

For the specific case of quantile regressions via momoments, the influence functions for the location, scale and quantile coefficients are:[^7]

[^7]: The derivation of the influence functions can be found in @sec-appendix.

$$\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\varepsilon|\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
$${#eq-ifs}

@@

The first, and most natural standard error estimator is given by equation @eq-eqvcv. This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators. Considering the location-scale model, the variance-covariance matrix for the quantile coefficients can be estimated as:

$$\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
 \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
  \end{pmatrix}
$$

This estimator of Standard errors should be robust to arbitrary heteroskedasticity. However, because the location-scale specification relies on the correct specification of the model heteroskedasticity, large differences in Standard errors compared to GLS-standard errors may be an indication of misspecification of the model.

@@

Because one of the typical applications of quantile regressions is the analysis of panel data, allowing for clustered standard errors at the individual level is important. If the unobserved error $\varepsilon$ is correlated within clusters, GLS-Standard errors could be severily biased. The standard recommendation has been to report block-bootstrap standard errors, clustering at the individual level.

Since we have access to the influence functions, it is straight forward to estimate one-way clustered standard errors.

Call $N_G$ to be the total number of clusteres g, where $g=1\dots N_G$. The clustered variance covariance matrix is given by:[^10]

[^10]: It should be noted that one could just as well apply the insights of @cameron_robust_2011, allowing for multiway clustering.

$$\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
$$

Where $S\lambda_i(\theta)$ is the sum of the influence functions over all observations within a given cluster $g$.

$$S\lambda_i(\theta) = \sum_{i\in g} \lambda_i(\theta)
$$

@@

The standard errors proposed by MSS can be understood as an application of generalized least squares (GLS), which will be valid as long as the model for heteroskedasticity is correctly specified.[^15] To estimate the GLS-Standard errors, we make use of the following property:

[^15]: As discussed in most econometric textbooks, like @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known, or can be estimated, is to use weighted least squares. While feasible, however, this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.

Consider the influence functions and robust variance-covariance matrix for the location coefficients:

$$\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
\end{aligned}
$$

Under the assumption that the model for heteroskedasticity is correctly specified, we can apply the law of iterated expectations and rewrite the variance-covariance matrix as:

$$\begin{aligned}
\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
\end{aligned}
$$

This standard error estimator is an application of GLS that accounts for the heteroskedasticity the model uses to identify the quantile coefficients. We can apply the same principle to find the GLS-Standard errors for the system of location-scale and quantile coefficients. To do this, define the following modified influence functions:

$$\begin{aligned}
\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
\tilde \lambda_{3,i}&=x_i' \gamma  \\
\tilde \psi_1 &= \varepsilon_i \\
\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
-  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
$$

Then, the GLS-Standard errors for the location-scale and quantile coefficients can be estimated as:

$$\hat{V}_{gls}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\varepsilon|\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
 \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
 \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
  \end{pmatrix}
$$

where

$$\begin{aligned}
\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
\end{aligned}
$$

This estimator of Standard errors is equivalent to the one derived by MSS by Theorem 3.

@@

2.  We estimate the location model using the centered-residualized variables:[^rc]

$$y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
$$

[^rc]: Using centered-residualized variables allow us to include a constant in the model specification, which simplifies the derivation of the influence functions. However, as with other fixed effects models, the constant is not identified, and thus should not be interpreted.

@@

$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}$$

@@

$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}$$

where $|\hat\nu_{i}|- \hat \omega_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$

@@

# Simulation Evidence

To show the performance of the extended strategy, we implement the results of a small simulation study. We consider a simple model with a single explanatory variable $x$, and a single fixed effect $g$. The data generating process is as follows:

# Illustrative application

In this section we replicate one of the excercises from MSS, allowing for time and individual fixed effects, as well as for different standard errors estimations. We use data from @persson_economic_2005, to estimate the relationship between surplus of goverment as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE), Share of population between 15-65 uears of age (P1564), the share of the population 65 years or older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars differntiating importer and exported countries (OILIM and OILEX); and the output gap (YGAP). In addition to country fixed effects (as illustrated in MSS), we also show results allowing for time fixed effects. @tbl-tb1 and  @tbl-tb2 provide the results for the model with and without time fixed effects, respectively. It show cases the location and scale coefficients, as well as the quantile coefficients for the 25th, 50th and 75th quantiles. We also report GLS-Standard errors, Robust standard errors (brackets) and clustered standard errors at the country level.

|            | polityt |       lyp |     trade |   p1564 |     p65 |      lspl |    oil\_im |    oil\_ex |      ygap |
| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
| Location   |           |           |           |           |           |           |           |           |           |
| \ coeff      |     0.116 |    -0.715 |     0.030 |     0.121 |     0.028 |     0.691 |    -0.047 |    -0.006 |     0.010 |
| \ se\_gls     |     0.046 |     0.540 |     0.008 |     0.033 |     0.070 |     0.035 |     0.008 |     0.022 |     0.028 |
| \ se\_r       |     0.047 |     0.597 |     0.008 |     0.031 |     0.070 |     0.037 |     0.007 |     0.017 |     0.021 |
| \ se\_cl      |     0.046 |     0.465 |     0.007 |     0.032 |     0.071 |     0.035 |     0.010 |     0.020 |     0.023 |
| Scale      |           |           |           |           |           |           |           |           |           |
| \ coeff      |    -0.097 |    -0.616 |     0.003 |     0.036 |     0.087 |    -0.085 |     0.013 |     0.016 |    -0.004 |
| \ se\_gls     |     0.032 |     0.371 |     0.005 |     0.023 |     0.048 |     0.024 |     0.006 |     0.015 |     0.019 |
| \ se\_r       |     0.031 |     0.398 |     0.005 |     0.020 |     0.049 |     0.025 |     0.005 |     0.010 |     0.015 |
| \ se\_cl      |     0.048 |     0.800 |     0.008 |     0.031 |     0.067 |     0.029 |     0.004 |     0.010 |     0.012 |
| Q25        |           |           |           |           |           |           |           |           |           |
| \ coeff      |     0.191 |    -0.239 |     0.028 |     0.093 |    -0.039 |     0.756 |    -0.057 |    -0.018 |     0.013 |
| \ se\_gls     |     0.059 |     0.684 |     0.010 |     0.042 |     0.088 |     0.045 |     0.010 |     0.027 |     0.035 |
| \ se\_r       |     0.056 |     0.656 |     0.008 |     0.036 |     0.086 |     0.040 |     0.010 |     0.020 |     0.025 |
| \ se\_cl      |     0.073 |     0.687 |     0.006 |     0.041 |     0.098 |     0.023 |     0.010 |     0.021 |     0.029 |
| Q50        |           |           |           |           |           |           |           |           |           |
| \ coeff      |     0.108 |    -0.765 |     0.030 |     0.124 |     0.035 |     0.684 |    -0.046 |    -0.005 |     0.009 |
| \ se\_gls     |     0.046 |     0.535 |     0.007 |     0.033 |     0.069 |     0.035 |     0.008 |     0.022 |     0.027 |
| \ se\_r       |     0.046 |     0.593 |     0.008 |     0.031 |     0.069 |     0.036 |     0.007 |     0.017 |     0.021 |
| \ se\_cl      |     0.043 |     0.484 |     0.008 |     0.032 |     0.070 |     0.036 |     0.010 |     0.020 |     0.023 |
| Q75        |           |           |           |           |           |           |           |           |           |
| \ coeff      |     0.031 |    -1.258 |     0.033 |     0.153 |     0.104 |     0.616 |    -0.036 |     0.008 |     0.006 |
| \ se\_gls     |     0.048 |     0.551 |     0.008 |     0.034 |     0.071 |     0.036 |     0.008 |     0.022 |     0.028 |
| \ se\_r       |     0.049 |     0.696 |     0.009 |     0.034 |     0.075 |     0.043 |     0.007 |     0.018 |     0.023 |
| \ se\_cl      |     0.039 |     0.919 |     0.012 |     0.041 |     0.079 |     0.055 |     0.010 |     0.022 |     0.020 |

: The determinants of government surpluses: Individual Fixed effects {#tbl-tb1}

As expected, @tbl-tb1 shows that point estimates for the point estimates for the quantile regressions are identical to the ones reported in @mss2019 (table 6), including analytical standard errors (GLS). With our estimator, however, we are able to also produce both robust and clustered standard errors for location and scale coefficients. Except for few cases, Robust and Clustered standard errors are larger than GLS standard errors, which may be an indication of misspecification of the model. The GLS standard errors we report differ from the ones in MSS, because they use panel standard errors, equivalent to our clustered standard errors, instead of the analytical standard errors we derive.

Considering the estimated effects across quantiles, we observe few differences in the reported GLS standard errors compared to the analytical standard errors reported MSS. Our clustered standard errors, however, are closer to the bootstrap based standard errors the authors report.[^20]

[^20]: There are two possible reasons that may explain the differences in the GLS standard errors. On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).

In @tbl-tb2, we report the results including both individual and year fixed effects. Because Oil prices only vary across years, the variableis excluded from the model specification. Accounting for time fixed effects, does not change the general conclusions one could make based no the results from @tbl-tb1. The two largest differences are that the log of income percapita has a positive effect on Goverment Surpluses, but only for the 25th quantile, because of the largest impact on the Scale component. Similarly, we observe that the income gap now has an impact on Goverment surplus that is always negative, but increasing across quantiles. In both instances, the effects are not statistically significant.

|            | polity |       lyp |     trade |  prop1564 |    prop65 |      lspl |      ygap |
| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
| Location   |           |           |           |           |           |           |           |
| \ coeff      |     0.126 |    -0.418 |     0.028 |     0.108 |     0.042 |     0.693 |    -0.014 |
| \ se\_gls     |     0.087 |     1.157 |     0.015 |     0.072 |     0.136 |     0.066 |     0.053 |
| \ se\_r       |     0.047 |     0.703 |     0.008 |     0.038 |     0.068 |     0.038 |     0.022 |
| \ se\_cl      |     0.048 |     0.506 |     0.008 |     0.044 |     0.077 |     0.037 |     0.022 |
| Scale      |           |           |           |           |           |           |           |
| \ coeff      |    -0.095 |    -1.255 |     0.005 |     0.033 |     0.040 |    -0.081 |     0.008 |
| \ se\_gls     |     0.081 |     1.073 |     0.014 |     0.067 |     0.126 |     0.061 |     0.049 |
| \ se\_r       |     0.031 |     0.452 |     0.005 |     0.025 |     0.045 |     0.025 |     0.017 |
| \ se\_cl      |     0.041 |     0.848 |     0.006 |     0.030 |     0.048 |     0.033 |     0.013 |
| Q25        |           |           |           |           |           |           |           |
| \ coeff      |     0.201 |     0.576 |     0.025 |     0.082 |     0.010 |     0.757 |    -0.020 |
| \ se\_gls     |     0.154 |     2.070 |     0.024 |     0.118 |     0.219 |     0.121 |     0.085 |
| \ se\_r       |     0.058 |     0.751 |     0.008 |     0.049 |     0.080 |     0.040 |     0.026 |
| \ se\_cl      |     0.073 |     0.761 |     0.006 |     0.052 |     0.087 |     0.023 |     0.027 |
| Q50        |           |           |           |           |           |           |           |
| \ coeff      |     0.119 |    -0.512 |     0.029 |     0.111 |     0.045 |     0.687 |    -0.013 |
| \ se\_gls     |     0.091 |     1.230 |     0.014 |     0.070 |     0.130 |     0.072 |     0.051 |
| \ se\_r       |     0.046 |     0.695 |     0.008 |     0.037 |     0.068 |     0.038 |     0.022 |
| \ se\_cl      |     0.045 |     0.529 |     0.008 |     0.044 |     0.077 |     0.039 |     0.021 |
| Q75        |           |           |           |           |           |           |           |
| \ coeff      |     0.041 |    -1.555 |     0.033 |     0.138 |     0.078 |     0.619 |    -0.007 |
| \ se\_gls     |     0.067 |     0.898 |     0.011 |     0.053 |     0.098 |     0.052 |     0.038 |
| \ se\_r       |     0.048 |     0.827 |     0.009 |     0.037 |     0.075 |     0.046 |     0.026 |
| \ se\_cl      |     0.038 |     0.980 |     0.012 |     0.050 |     0.086 |     0.063 |     0.020 |
: The determinants of government surpluses: Individual and Time Fixed effects {#tbl-tb2}

@@

# Appendix {.appendix}{#sec-appendix}
